SDR enhancement by clouds

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 22:14

abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.

@@

@@

CE and ECE usefulness

@@

The use of the actual modeled values of clear sky GHI can not provide us with a
robust method to distinguish the CE cases.

To select the exact values of the threshold used (Equation \ref{eq:CE4}), we implemented manual inspection of the CE indemnification, on specially selected days from the whole dataset. 
We used seven sets of random selected days, with characteristics relevant to the efficiency of the threshold.

six criteria 
in order to evaluate random groups of about 20 to 30 days with some characteristics

- 20 days with the largest over irradiance CE events
- 30 days with largest total over irradiance
- 20 days without clouds (CSid) @Natsis2023
- any day without clouds and EC events
- 20 days with at least 60% of day length without clouds and some EC events
- 30 random days
- some manual selected days that were included during the manual inspection

For some of this edge cases we further use images from a sky-cam, in order to evaluate our selection of the thresholds.

Thresholds by inspecting a selection of days with some specs......

Reasoning for the selection...........

>>>>

# abstract: |
#   This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.

@@

# Abstract {.unnumbered}

- Phenomenon
- Effects
- bibliography
- our approach
- our results

@@

CE and ECE usefulness 
importance
problems

reported trends

CE mechanism

@@

The use of the actual modeled values of clear sky GHI can not provide us with a
robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs,
thus we used a relative factor, to create an upper envelope of the clear sky
irradiance, above which, any GHI value can safely attributed to CE.

To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
manual inspection of the CE identification, on specially selected days from the whole
dataset.  We used seven sets of selected days, with characteristics relevant to the
efficiency of the identification threshold.  These sets were  random groups of about
20 to 30 days with the following characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
(d) without clouds and without EC events,
(e) with at least $60\%$ of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.

<!-- - some manual selected days that were included during the manual inspection -->
<!-- - 20 days with the largest over irradiance CE events -->
<!-- - 30 days with largest total over irradiance -->
<!-- - 20 days without clouds (CSid) @Natsis2023 -->
<!-- - any day without clouds and EC events -->
<!-- - 20 days with at least 60% of day length without clouds and some EC events -->
<!-- - 30 random days -->
<!-- - some manual selected days that were included during the manual inspection -->

Where it was needed, for some of edge cases, we also used images from a sky-cam,
along with the manual inspection.

Reasoning for the  final selection...........
